Thermodynamic response functions in a cell fluid model

### 2024-08-07 main_morse_response_functions.tex

\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
\usepackage{amssymb}
\usepackage{physics}
\usepackage{cite} % may be useful for different formats of numerical citation
\usepackage{hyperref} % for hyperlinks in references

\usepackage{caption} % for \caption*

%**************
%\usepackage[pdftex]{graphicx}
%\usepackage{amsmath}    % for "\eqref" macro
\usepackage{graphicx}
%**************

@@

	The coefficients $g_n$ are given by the formulas:
	\begin{align}
		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2,
	\end{align}
	where $T_n(p,\alpha^*)$ are the following special functions
	\begin{equation}
	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
	\end{equation}
	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
	\begin{equation}
	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
	\end{equation} 
	Note that we denote $\beta_c$ as the inverse critical temperature. Since $p$ fails to be the function of temperature, the coefficients $g_n$ are also temperature-free. The quantity $\tilde D(0)$ which has already appeared in both equations \eqref{eq:eos} and \eqref{chem_pot} is a function of temperature
	\begin{equation}
	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)},
	\end{equation}
	which equals zero at $T=T_c$. This circumstance gives us an expression for determining the critical temperature 
	\begin{equation}
		T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
	\end{equation}    
	The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by
	\begin{align}
		& E_\mu (M, T) = - \frac{1}{2 N_v} \ln (2\pi \beta W(0)) +  g_0 - \frac{\beta W(0)}{2} \!\! \left( \! \frac{\tilde\mu}{W(0)} \! \right)^{\! 2} \!\!\! - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
	\end{align}
	Note that for all $ \tau> 0 $ there are no restrictions on the value of $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
	\begin{equation}\label{2d18}
	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
	\end{equation}
	where
	\begin{equation}
	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3\bar{M}}{g_4}\right)^2, \qquad g_4<0.
	\end{equation}  
	...
	\begin{equation}\label{3d3}
	\bar n = n_g - \bar{M} + \tilde g_2 \gamma_\tau \bar \rho_0,
	\end{equation}
	where
	\begin{equation}\label{3d4}
	n_g = g_1 + n_c \tilde g_2 - \frac{1}{6} g_3^3 / g_4^2.
	\end{equation}
	...

>>>>

\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
\usepackage{amssymb}
\usepackage{physics}
\usepackage{cite} % may be useful for different formats of numerical citation
\usepackage{hyperref} % for hyperlinks in references
\usepackage{caption} % for \caption*
\usepackage{amsmath}    % for "\eqref" macro
\usepackage{graphicx}

@@

	The coefficients $g_n$ are given by the formulas:
	\begin{align}
		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, \\
		& n_c = -g_3/g_4, \nonumber
	\end{align}
	where $T_n(p,\alpha^*)$ are the following special functions
	\begin{equation}
	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
	\end{equation}
	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
	\begin{equation}
	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
	\end{equation} 
	The quantity $\beta_c$ denotes the critical value of the inverse temperature.
	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature. The numerical values for other coefficients used in this paper are the same as those in~\cite{KozlovskiiDobush2020}:
	\begin{equation*}
		\alpha^* = 5.0, \quad \gamma = 1.65, \quad n_0 = 1.521.
	\end{equation*}

	The quantity $\tilde D(0)$ entering equations~\eqref{eq:eos} and~\eqref{chem_pot} is a function of temperature
	\begin{equation}
	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
	\end{equation}
	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite{KozlovskiiDobush2020}
	\begin{equation}
		T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
	\end{equation}

	The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by
	\begin{align}
		& E_\mu (M, T) = - \frac{1}{2 N_v} \ln (2\pi \beta W(0)) +  g_0 - \frac{\beta W(0)}{2} \!\! \left( \! \frac{\tilde\mu}{W(0)} \! \right)^{\! 2} \!\!\! - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
	\end{align}
	Note that for all $ \tau> 0 $ there are no restrictions on the value of $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
	\begin{equation}\label{2d18}
	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
	\end{equation}
	where
	\begin{equation}
	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3\bar{M}}{g_4}\right)^2, \qquad g_4<0.
	\end{equation}  
	...
	\begin{equation}\label{3d3}
	\bar n = n_g - \bar{M} + \tilde g_2 \gamma_\tau \bar \rho_0,
	\end{equation}
	where
	\begin{equation}\label{3d4}
	n_g = g_1 + n_c \tilde g_2 - \frac{1}{6} g_3^3 / g_4^2.
	\end{equation}
	...
